Manuscript

### 2019-01-09 manuscript_analysis.Rmd
p.adj and rewriting, add code to papaja doc

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "FDR_cutoff")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

@@

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

# All
g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                               Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
                               Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
                               Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
                               Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
```

@@

ccle_dgl_summ <- ccle_signif_grid_lineage
ccle_dgl_summ$Drug_Gene <- paste0(ccle_dgl_summ$Drug, "_", ccle_dgl_summ$Hugo_Symbol)
ccle_dgl_summ <- merge(g2p_dgl_mut_tally, ccle_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_dgl_summ$Drug_Gene_Lin <- paste0(ccle_dgl_summ$Drug_Gene, "_", ccle_dgl_summ$group_general_lineage_name)
ccle_dgl_summ$n <- ifelse(is.na(ccle_dgl_summ$n), 0, ccle_dgl_summ$n)
ccle_dgl_summ$InG2P <- ifelse(ccle_dgl_summ$n != 0, "Yes", "No")
ccle_dgl_summ$Dataset <- "CCLE"

ctrp_dgl_summ <- ctrp_signif_grid_lineage
ctrp_dgl_summ$Drug_Gene <- paste0(ctrp_dgl_summ$Drug, "_", ctrp_dgl_summ$Hugo_Symbol)
ctrp_dgl_summ <- merge(g2p_dgl_mut_tally, ctrp_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ctrp_dgl_summ$Drug_Gene_Lin <- paste0(ctrp_dgl_summ$Drug_Gene, "_", ctrp_dgl_summ$group_general_lineage_name)
ctrp_dgl_summ$n <- ifelse(is.na(ctrp_dgl_summ$n), 0, ctrp_dgl_summ$n)
ctrp_dgl_summ$InG2P <- ifelse(ctrp_dgl_summ$n != 0, "Yes", "No")
ctrp_dgl_summ$Dataset <- "CTRP"

gdsc_dgl_summ <- gdsc_signif_grid_lineage
gdsc_dgl_summ$Drug_Gene <- paste0(gdsc_dgl_summ$Drug, "_", gdsc_dgl_summ$Hugo_Symbol)
gdsc_dgl_summ <- merge(g2p_dgl_mut_tally, gdsc_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
gdsc_dgl_summ$Drug_Gene_Lin <- paste0(gdsc_dgl_summ$Drug_Gene, "_", gdsc_dgl_summ$group_general_lineage_name)
gdsc_dgl_summ$n <- ifelse(is.na(gdsc_dgl_summ$n), 0, gdsc_dgl_summ$n)
gdsc_dgl_summ$InG2P <- ifelse(gdsc_dgl_summ$n != 0, "Yes", "No")
gdsc_dgl_summ$Dataset <- "GDSC"

>>>>

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
crispr_signif_g2p_gene_kable <- knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj", "k", "FDR_cutoff")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r}
test <- p.adjust(ccle_signif_g2p$p, method = "BH")
```

@@

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
# ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
# ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
# ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
# ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
# ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
# ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
# ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
# ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
# ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
# ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
# ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
# ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
# ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
# ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
# ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
# ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
# gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
# gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
# gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
# gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
# gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
# gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
# gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
# gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

# All
g2p_cor <- rbind(ccle_cor_res, ctrp_cor_res, gdsc_cor_res)
g2p_cor$Pearson_GE_Abs <- abs(g2p_cor$Pearson_Corr_GE)
g2p_cor$Pearson_GE_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_GE) == -1, "-", "0"))
g2p_cor$Pearson_CN_Abs <- abs(g2p_cor$Pearson_Corr_CN)
g2p_cor$Pearson_CN_Sign <- ifelse(sign(g2p_cor$Pearson_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Pearson_Corr_CN) == -1, "-", "0"))
g2p_cor$Spearman_GE_Abs <- abs(g2p_cor$Spearman_Corr_GE)
g2p_cor$Spearman_GE_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_GE) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_GE) == -1, "-", "0"))
g2p_cor$Spearman_CN_Abs <- abs(g2p_cor$Spearman_Corr_CN)
g2p_cor$Spearman_CN_Sign <- ifelse(sign(g2p_cor$Spearman_Corr_CN) == 1, "+", ifelse(sign(g2p_cor$Spearman_Corr_CN) == -1, "-", "0"))
# g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
#                                Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE),
#                                Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN),
#                                Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE),
#                                Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
```

@@

ccle_dgl_summ <- ccle_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
ccle_dgl_summ$Drug_Gene <- paste0(ccle_dgl_summ$Drug, "_", ccle_dgl_summ$Hugo_Symbol)
ccle_dgl_summ <- merge(g2p_dgl_mut_tally, ccle_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ccle_dgl_summ$Drug_Gene_Lin <- paste0(ccle_dgl_summ$Drug_Gene, "_", ccle_dgl_summ$group_general_lineage_name)
ccle_dgl_summ$n <- ifelse(is.na(ccle_dgl_summ$n), 0, ccle_dgl_summ$n)
ccle_dgl_summ$InG2P <- ifelse(ccle_dgl_summ$n != 0, "Yes", "No")
ccle_dgl_summ$Dataset <- "CCLE"

ctrp_dgl_summ <- ctrp_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
ctrp_dgl_summ$Drug_Gene <- paste0(ctrp_dgl_summ$Drug, "_", ctrp_dgl_summ$Hugo_Symbol)
ctrp_dgl_summ <- merge(g2p_dgl_mut_tally, ctrp_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
ctrp_dgl_summ$Drug_Gene_Lin <- paste0(ctrp_dgl_summ$Drug_Gene, "_", ctrp_dgl_summ$group_general_lineage_name)
ctrp_dgl_summ$n <- ifelse(is.na(ctrp_dgl_summ$n), 0, ctrp_dgl_summ$n)
ctrp_dgl_summ$InG2P <- ifelse(ctrp_dgl_summ$n != 0, "Yes", "No")
ctrp_dgl_summ$Dataset <- "CTRP"

gdsc_dgl_summ <- gdsc_signif_grid_lineage %>% separate(Drug_Gene_Lin, c("Drug", "Hugo_Symbol", "group_general_lineage_name"), "_")
gdsc_dgl_summ$Drug_Gene <- paste0(gdsc_dgl_summ$Drug, "_", gdsc_dgl_summ$Hugo_Symbol)
gdsc_dgl_summ <- merge(g2p_dgl_mut_tally, gdsc_dgl_summ[, c("Drug_Gene", "group_general_lineage_name", "p")], by = c("Drug_Gene", "group_general_lineage_name"), all.y = TRUE)
gdsc_dgl_summ$Drug_Gene_Lin <- paste0(gdsc_dgl_summ$Drug_Gene, "_", gdsc_dgl_summ$group_general_lineage_name)
gdsc_dgl_summ$n <- ifelse(is.na(gdsc_dgl_summ$n), 0, gdsc_dgl_summ$n)
gdsc_dgl_summ$InG2P <- ifelse(gdsc_dgl_summ$n != 0, "Yes", "No")
gdsc_dgl_summ$Dataset <- "GDSC"
